Sequoidal Categories and Transfinite Games: Towards a Coalgebraic Approach to Linear Logic\footnote{This work was partially supported by [TODO: find the appropriate grant codes]}

### 2017-05-08 round-corner/paper/lipics-v2016-authors/jim1/sequoidal (1).tex
A whole bunch of things.

%% Other macros
\newcommand*\from{\colon}
\def \inv {^{-1}}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\pr}{pr}
\newcommand{\Rel}{{\mathsf{Rel}}}
\newcommand{\inr}{{\mathsf{inr}}}
\newcommand{\inl}{{\mathsf{inl}}}
\newcommand{{\Na}}{{\mathbb{N}}}
\newcommand{{\cell}}{{\mathsf{cell}}}
\newcommand{\tr}{\oslash}
\newcommand{\fix}{{\mathsf{fix}}}
\newcommand{\eq}{{\mathsf{eq}}}
%\\write{{\mathtt{write}}}
\def\read{{\mathtt{read}}}
\def\({\ensuremath{( \! [}}
\def\){\ensuremath{] \! )}}
\newcommand{\perm}{{\mathsf{perm}}}
\newcommand{\tensor}{\otimes}
\newcommand{\sequoid}{\oslash}
\renewcommand{\implies}{\multimap}
\newcommand{\comp}[2]{#1 \circ #2}
\newcommand{\cprd}{\sqcup}
\newcommand{\bigcprd}{\bigsqcup}
\newcommand{\C}{\mathcal C}
\newcommand{\F}{\mathcal F}
\newcommand{\G}{\mathcal G}
\newcommand{\suchthat}{\;\colon\;}
\newcommand{\varsuchthat}{\;\mid\;}
\newcommand{\OP}{\{O,P\}}
\newcommand{\emptyplay}{\epsilon}
\newcommand{\prefix}{\sqsubseteq}
\newcommand{\pprefix}{\sqsubsetneqq}
\newcommand{\ppprefix}{\sqsubset}
\DeclareMathOperator{\assoc}{assoc}
\DeclareMathOperator{\lunit}{lunit}
\DeclareMathOperator{\runit}{runit}
\DeclareMathOperator{\sym}{sym}
\newcommand{\braid}{\sym}
\newcommand{\blank}{\;\underline{\hspace{1.5ex}}\;}
\newcommand{\der}{{\mathtt{der}}}
\newcommand{\mult}{{\mathtt{mult}}}
\DeclareMathOperator{\wk}{wk}
\newcommand{\toisom}{{\xrightarrow{\cong}}}
\newcommand{\passoc}{{\mathtt{passoc}}}
\newcommand{\pcomm}{{\mathtt{pcomm}}}
\newcommand{\run}{{\mathtt{r}}}
\newcommand{\lun}{{\mathtt{l}}}
\newcommand{\fcoal}[1]{{\leftmoon #1 \rightmoon}}
\renewcommand{\subset}{\subseteq}
\let\oldemptyset\emptyset
\let\emptyset\varnothing
\newcommand{\s}{\mathfrak{s}}
\newcommand{\dist}{{\mathtt{dist}}}
\newcommand{\dec}{{\mathtt{dec}}}
\renewcommand{\int}{{\mathtt{int}}}
\DeclareMathOperator{\CCom}{CCom}
\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
\newcommand{\Set}{\catname{Set}}
\newcommand{\Ord}{\catname{Ord}}
\newcommand\oppcat[1]{#1^{\mathrm{op}}}

@@

\begin{definition}
  Let $\C=(\C,\C_s,J,\wk)$ be a sequoidal category.  We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategory of $\C$ containing all isomorphisms and finite products of $\C$, and the morphisms $\wk_{A,B}$ and $J$ is the inclusion functor.

%  If $\C$ is an inclusive sequoidal category, we say that $\C$ is \emph{Cartesian} if $\C_s$ has all products and these are preserved by $J$.
 We say that $\C$ is \emph{decomposable} if it is affine, and for any $A$ and $B$, the tensor product $A \otimes B$ is a cartesian product of $A \tr B$ and $B \tr A$, with projections $\wk_{A,B}:A \otimes B \rightarrow A \tr B$ and  $\comp{\wk_{A,B}}{\sym_{A,B}}:A \otimes B \rightarrow B \tr A$, and if the product $A \times B$ exists, then $(A \times B) \sequoid C$ is the product of $A \sequoid C$ and $B \sequoid C$, with projections $\pi_l \sequoid C,\pi_r \sequoid C$. 
So if $\C$ has all finite products, 
the natural transformations
  \begin{gather*}
    \dec_{A,B} = \langle \wk_{A,B}, \comp{\wk_{A,B}}{\sym_{A,B}}\rangle\from A\tensor B\to (A\sequoid B)\times (B\sequoid A) \\
   % \dec^0 \from I \to 1 \\
    \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
    \dist_{A,0}\from 1\sequoid A\to 1
  \end{gather*}
  are isomorphisms.
\end{definition}

@@

In any inclusive sequoidal category with a cofree exponential we have  a  $A \tr\_$-coalgebra  $\alpha:!A \rightarrow A \tr !A =  \delta;(\eta \otimes !A);\wk_{A \tr !A}$. In our category of games this
%  The sequoidal exponential $\oc A$, together with the obvious copycat strategy $\alpha\from\oc A\to A\sequoid\oc A$, 
is the final coalgebra for the endofunctor $A\sequoid\blank$.  In other words, if $B$ is a negative game and $\sigma\from B\to A\sequoid B$ is a morphism then there is a unique morphism $\fcoal{\sigma}\from B\to \oc A$ such that the following diagram commutes:
  \[
    \begin{tikzcd}
      B \arrow[r, "\sigma"] \arrow[d, "\fcoal{\sigma}"']
        & A \sequoid B \arrow[d, "\id_A\sequoid\fcoal{\sigma}"] \\
      \oc A \arrow[r, "\alpha"']
        & A \sequoid \oc A
    \end{tikzcd}
    \]
\end{proposition}
\begin{proof}
  See \cite{martinsthesis}.  We shall shortly give a proof in the more general case.
\end{proof}

@@

We want to construct  $\oc A\xrightarrow{\mu}\oc A\tensor\oc A$ from the final $A\sequoid\blank$-coalgebra, $(\oc A,\alpha)$, and show that it is the cofree commutative comonoid on $A$.  It turns out that we shall need one more fact about the category of games to prove this.

@@

\subsection{The Sequoidal Exponential as a Bifree Algebra}
Observe that in our category of games, $(!A,\alpha)$ is in fact a \emph{bifree algebra} for $A\tr\_$ --- the isomorphism $\alpha^{-1}: A \tr !A \rightarrow !A$ is an initial algebra for  $A \tr \_$.  We may show that in such cases, the condition that $!$ is strong monoidal --- and thus the cofree exponential ---  always holds\footnote{Without requiring our sequoidally decomposable category to have finite products  we may equip each object $!A$ with the structure of a comonoid by defining:   
$\delta:!A \rightarrow !A  \otimes !A$
 to be the catamorphism of the $A \tr \_$ algebra:
$$A \tr (!A \otimes !A) %\stackrel{\langle \id, A \tr \sym\rangle}{\cong} 
\cong A \tr (!A \otimes !A) \times  A \tr (!A \otimes !A) \cong (A \tr !A) \tr !A \times  (A \tr !A) \tr !A \cong (!A \tr !A) \cong (!A \tr !A) \cong (!A \otimes !A)$$     
This satisfies the further requirements of a \emph{linear category} in the sense of \cite{Bierman}, although it does not appear to be possible to show that it is the cofree commutative comonoid.} :
we may define an inverse to $\int:!A \otimes !A \rightarrow ! (A \times B)$  as the \emph{catamorphism} of the  $A \tr\_$-algebra:
$$(A \times B) \tr !A \otimes !B \cong (A \tr (!A \otimes !B)) \times  (B \tr (!A \otimes !B)) \cong (!A \tr !B) \times (!B \tr !A)$$

It is not necessary for the final $A \tr\_$-coalgebra to be bifree for the exponential to be strong monoidal and thus the cofree commutative comonoid. An example is provided by  the category of games with winning conditions and winning strategies, which is sequoidal closed and decomposable. To show that the  final $A \tr\_$-coalgebra in this category is not bifree, it suffices to observe that from such an algebra, we may derive a  \emph{fixed point} operator $\fix_A:\C(A,A) \rightarrow \C(I,A)$ for each $A$, such that $\fix_A(f);f = \fix(f)$.      
\begin{proposition}Suppose $\C$ is sequoidal closed and decomposable, and $(!A,\alpha)$ is a bifree $A \tr\_$-algebra. Then we may define a fixed point operator on $\C$.  
\end{proposition}    
\begin{proof}For any $A$, let  $\Phi_A:!(A \multimap A) \rightarrow A$ be the catamorphism of the counit to the adjunction $A \tr\_ \dashv A \multimap$,  $\epsilon_{A,A}: (A \multimap A) \tr A \rightarrow A$, which is a  $(A \multimap A) \tr \_$-algebra. For any morphism $f:A \rightarrow A$ we may define $\fix_A(f) = \Lambda(f)^\dag;\Phi_A$, where $\Lambda(f):I \rightarrow (A \multimap A)$ is the ``name'' of $f$.    
\end{proof}
As one would expect, it is not possible to define a fixed point operator on the category of games and winning strategies ---  for example, if $\bot$ is the game with a single move then the hom-set $\C(I,\bot)$ is empty and hence there can be no morphism $\fix_\bot(\id_\bot)$. So the final  $A \tr \_$-coalgebra is not bifree in this case.

\subsection{A formula for the sequoidal exponential}
We now consider an alternative construction of the cofree commutative comonoid in a sequoidally decomposable category, which leads to some illuminating comparisons with the coalgebraic approach. It is based on the formula  given by 
Melli\'es, Tabareau and Tasson \cite{MTT}, which does not depend on the presence of cartesian products, but obtains the cofree commutative comonoid as a limit of \emph{symmetric tensor powers}.
\begin{definition}If $A$ is an object in a symmetric monoidal category, a $n$-fold symmetric tensor power of $A$ is an  \emph{equalizer} $(A^n,\eq)$ for the group $G$ of symmetry automorphisms on $A^{\otimes n}$. A tensor power is preserved by the tensor product if $(B\otimes A^n,\eq \otimes B)$ is an equalizer for the automorphisms $\{B \otimes g\ |\ g \in G\}$.
\end{definition}
In any affine category\footnote{This is a special case of the situation considered in  \cite{MTT}: that $A$ is a ``free pointed object''.} with tensor powers of $A$ we may define a diagram $\Delta(A) = $
$$I \stackrel{p_0}{\leftarrow} A \stackrel{p_1}{\leftarrow} A^2 \ldots A^i \stackrel{p_i}{\leftarrow} A^{i+1} \ldots$$
where   
$p_i:A^{i+1} \rightarrow A^i$ is the unique morphism given by the universal property of the symmetric tensor power,  such that $p_i;\eq_i:A^{i+1} \rightarrow A^{\otimes i} = \eq_{i+1};(A^{\otimes i} \otimes t_A)$.

Melli\'es, Tabareau and Tasson \cite{MTT} have shown that where the limit $(A^\infty, \{p^\infty_i:A^\infty \rightarrow A^i\}$ for this diagram exists  and commutes with the tensor,  --- i.e. for each object $B$, $B \otimes A^\infty$ is the limit of 
$$B \otimes I \stackrel{B \otimes p_0}{\leftarrow} B \otimes A  \stackrel{B \otimes p_1}{\leftarrow} B\otimes  A^2 \ldots $$
then a comultiplication $\delta:A^\infty \rightarrow A^\infty \otimes A^\infty$ may be defined making $(A^\infty,\delta,t_{!A})$ the cofree commutative comonoid. Where these conditions are satisfied, we shall call this a MTT-exponential.   
\begin{proposition}Any sequoidally decomposable category has all symmetric tensor powers, and these are preserved by the tensor.  
\end{proposition} 
\begin{proof}
By sequoidal decomposability, for any $n$, $A^{\otimes (n+1)}$ is the cartesian product $\Pi_{i \leq n} (A \tr A^{\otimes n})$ with projections 
  $\comp{\sym_i}{\wk_{A,A^{\otimes n}}} $, where  $\sym_i: A^{\tensor (n+1)} \rightarrow A^{\tensor (n+1)}$ is the symmetry isomorphism corresponding to the permutation on $n$ which swaps $1$ and $i$.

  We inductively define the sequoid powers $A^{\sequoid n}$ by $A^{\sequoid 1}=A$ and $A^{\sequoid(n+1)}=A\sequoid A^{\sequoid n}$.  Given $n$, we inductively define a morphism $\eq_n\from A^{\sequoid n}\to A^{\tensor n}$ as the diagonal $\langle \id_A\sequoid\eq_{n-1}\rangle$ into the product -- so $\comp{\wk}{\comp{\sym_i}{\eq_n}}=\id\sequoid e_{n-1}$ for each $i$.

  If $\pi\in S_n$ is a permutation, we write $\sym^\pi$ for the appropriate symmetry of $A^{\tensor n}$.  We now claim that $\comp{\sym^\pi}{\eq_n}=\eq_n$ for all $\pi\in S_n$ -- so $\eq_n$ equalizes the $\sym^\pi$.  Indeed, let $\pi\in S_n$.  Then we may write $\sym^\pi = \comp{\id_A\tensor\sym^\rho}{\sym_i}$ for some $i$ and some $\rho\in S_{n-1}$.  Now we have:
  \begin{IEEEeqnarray*}{rClC}
    \comp{\wk}{\comp{\sym^\pi}{\eq_n}} & = & \comp{\wk}{\comp{\comp{(\id\tensor\sym^\rho)}{\sym_i}}{\eq_n}} & \\
    & = & \comp{(\id\sequoid\sym^\rho)}{\comp{\wk}{\comp{\sym_i}{\eq_n}}} & \hspace{24pt}\textrm{(by naturality of $\wk$)} \\
    & = & \comp{(\id\sequoid\sym^\rho)}{(\id\sequoid\eq_{n-1})} & \\
    & = & \id\sequoid\eq_{n-1}
  \end{IEEEeqnarray*}
  Since $\pi$ was arbitrary, it follows that $\comp{\wk}{\comp{\comp{\sym_j}{\sym^{\pi}}}{\eq_n}}=\comp{\comp{\wk}{\sym_j}}{\eq_n}$ for all $j$ and therefore that $\comp{\sym^\pi}{\eq_n}=\eq_n$ for all $\pi$, as desired.

  Now define $\wk^n\from A^{\sequoid n}\to A^{\tensor n}$ inductively by $\wk^n = \comp{\id\sequoid\wk^{n-1}}{\wk}$.  We may show by induction that $\comp{\wk^n}{\eq_n}=\id_{A^{\sequoid n}}$ for all $n$: indeed, we have
  \begin{IEEEeqnarray*}{rClC}
    \comp{\wk^n}{\eq_n} & = & \comp{(\id\sequoid\wk^{n-1})}{\comp{\wk}{\eq_n}} & \\
    & = & \comp{(\id\sequoid\wk^{n-1})}{(\id\sequoid\eq_{n-1})} & \\
    & = & \id\sequoid \id = \id & \hspace{24pt}\textrm{(by induction)}
  \end{IEEEeqnarray*}
  Now let $f\from C \to B \tensor A^{\tensor n}$ be such that $\comp{(\id\tensor\sym^\pi)}{f}=f$ for all $\pi\in S_n$.  It follows from what we have just shown that if $f=\comp{(\id\tensor\eq_n)}{g}$, then $g=\comp{\comp{\id\tensor\wk^n}{\id\tensor\eq_n}}{g}=\comp{\id\tensor\wk^n}{f}$.  So we just need to show that
  \[
    f=\comp{(\id\tensor(\comp{\eq_n}{\wk_n}))}{f}
    \]
  We first assume that $B=I$, so we have $f\from C\to B\tensor A^{\tensor n}$ and $\comp{\sym^\pi}{f}=f$ for all $\pi\in S_n$ and we are trying to show that $f=\comp{\comp{\eq_n}{\wk^n}}{f}$.  We do this by showing that $\comp{\comp{\wk}{\sym_i}}{\comp{\comp{\eq_n}{\wk^n}}{f}}=\comp{\comp{\wk}{\sym_i}}{f}$ for all $i$.

  Indeed, we have:
  \begin{IEEEeqnarray*}{rClC}
    \comp{\comp{\wk}{\sym_i}}{\comp{\comp{\eq_n}{\wk^n}}{f}} & = & \comp{\comp{(\id\sequoid\eq_{n-1})}{(\id\sequoid\wk^{n-1})}}{\comp{\wk}{f}} & \\
    & = & \comp{\wk}{\comp{(\id\tensor(\comp{\eq_{n-1}}{\wk^{n-1}}))}{f}} &\hspace{24pt}\textrm{(by naturality of $\wk$)} \\
    & = & \comp{\wk}{f} &\hspace{2pt}\textrm{(by induction)} \\
    & = & \comp{\wk}{\comp{\sym_i}{f}}
  \end{IEEEeqnarray*}

  Now let $B$ be an arbitary object of the category.  [TODO: finish working this out.]
\end{proof}
Thus, in any sequoidally decomposable category, the diagram $\Delta(A)$ exists for any $A$. If a limit for this diagram exists and is preserved by the sequoid, 
--- i.e. for any $B$, $B \tr A^\infty$ is the limit for $B \tr \Delta(A)$ --- then it is preserved by the tensor, and is therefore the cofree commutative comonoid. Conversely, we may show that any cofree commutative comonoid which arises as a $\otimes$-preserving limit of symmetric tensor powers is a final coalgebra.  
\begin{proposition}If a sequoidally decomposable category has a MTT-exponential, then $(A^\infty,\delta;(\eta \otimes !A);\wk_{A \tr !A})$ is a final coalgebra for the functor $A \tr \_$.    
\end{proposition}
\begin{proof}
  Observe that in a sequoidally decomposable category, the morphism $\wk_{A,A^n}:A \tr A^n: \rightarrow A^{n+1}$ is a section (we may define the corresponding retraction inductively from the decomposition of the tensor).   Hence if   the limit $A^\infty$ is preserved by the functor $A \otimes \_$, it is preserved by the sequoid $A \tr\_$ --- i.e. $A^\infty$ is the limit of the chain $A \tr \Delta = \Delta$.

Thus, for  any  $A \tr\_$-coalgebra $f:B \rightarrow A \tr B$, we may define a unique coalgebra morphism $\(f\):B \rightarrow !A$ as the mediating morphism of the cone $\{f_i:B \rightarrow A^i\ |\ i \in \omega\}$, where  $f_0 = t_B$ and $f_{i+1} = f;(A \tr f_i)$.  
\end{proof}

@@

It is well known (see \cite{finalseq}, for instance) that if $j_\delta^{\delta+1}$ is an isomorphism for some $\delta$, then ${j_\delta^{\delta+1}}\inv\from A^{\sequoid\delta}\to A\sequoid A^{\sequoid\delta}$ is the final coalgebra for the functor $A\sequoid\blank$.  In this case, we say that the sequence \emph{stabilizes at $\delta$}.  Our proof strategy is therefore to show that the sequence stabilizes at some $\delta$, and to show that $A^{\sequoid\delta}$ is isomorphic to $\oc A$.

>>>>

%% Other macros
\newcommand*\from{\colon}
\def \inv {^{-1}}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\pr}{pr}
\newcommand{\Rel}{{\mathsf{Rel}}}
\newcommand{\inr}{{\mathsf{inr}}}
\newcommand{\inl}{{\mathsf{inl}}}
\newcommand{{\Na}}{{\mathbb{N}}}
\newcommand{{\cell}}{{\mathsf{cell}}}

%\\write{{\mathtt{write}}}
\def\read{{\mathtt{read}}}

\newcommand{\tensor}{\otimes}
\newcommand{\sequoid}{\oslash}
\renewcommand{\implies}{\multimap}
\newcommand{\comp}[2]{#1 \circ #2}
\newcommand{\cprd}{\sqcup}
\newcommand{\bigcprd}{\bigsqcup}
\newcommand{\C}{\mathcal C}
\newcommand{\F}{\mathcal F}
\newcommand{\G}{\mathcal G}
\newcommand{\suchthat}{\;\colon\;}
\newcommand{\varsuchthat}{\;\mid\;}
\newcommand{\OP}{\{O,P\}}
\newcommand{\emptyplay}{\epsilon}
\newcommand{\prefix}{\sqsubseteq}
\newcommand{\pprefix}{\sqsubsetneqq}
\newcommand{\ppprefix}{\sqsubset}
\DeclareMathOperator{\assoc}{assoc}
\DeclareMathOperator{\lunit}{lunit}
\DeclareMathOperator{\runit}{runit}
\DeclareMathOperator{\sym}{sym}
\newcommand{\braid}{\sym}
\newcommand{\blank}{\;\underline{\hspace{1.5ex}}\;}
\newcommand{\der}{{\mathtt{der}}}
\newcommand{\mult}{{\mathtt{mult}}}
\DeclareMathOperator{\wk}{wk}
\newcommand{\toisom}{{\xrightarrow{\cong}}}
\newcommand{\passoc}{{\mathtt{passoc}}}
\newcommand{\pcomm}{{\mathtt{pcomm}}}
\newcommand{\run}{{\mathtt{r}}}
\newcommand{\lun}{{\mathtt{l}}}
\newcommand{\fcoal}[1]{{\leftmoon #1 \rightmoon}}
\renewcommand{\subset}{\subseteq}
\let\oldemptyset\emptyset
\let\emptyset\varnothing
\newcommand{\s}{\mathfrak{s}}
\newcommand{\dist}{{\mathtt{dist}}}
\newcommand{\dec}{{\mathtt{dec}}}
\renewcommand{\int}{{\mathtt{int}}}
\DeclareMathOperator{\CCom}{CCom}
\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
\newcommand{\Set}{\catname{Set}}
\newcommand{\Ord}{\catname{Ord}}
\newcommand\oppcat[1]{#1^{\mathrm{op}}}

@@

\begin{definition}
  Let $\C=(\C,\C_s,J,\wk)$ be a sequoidal category.  We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategory of $\C$ containing the monoidal isomorphisms and the morphisms $\wk_{A,B}$, $J$ is the inclusion functor and $J$ reflects isomorphisms.

S

%  If $\C$ is an inclusive sequoidal category, we say that $\C$ is \emph{Cartesian} if $\C_s$ has all products and these are preserved by $J$.
  In that case, we say that $\C$ is \emph{decomposable} if the natural transformations
  \begin{gather*}
    \dec_{A,B} = \langle \wk_{A,B}, \comp{\wk_{A,B}}{\sym_{A,B}}\rangle\from A\tensor B\to (A\sequoid B)\times (B\sequoid A) \\
    \dec^0 \from I \to 1
  \end{gather*}
  are isomorphisms and we say that $\C$ is \emph{distributive} if the natural transformations
  \begin{gather*}
    \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
    \dist_{A,0}\from 1\sequoid A\to 1
  \end{gather*}
  are isomorphisms.
\end{definition}

@@

  The sequoidal exponential $\oc A$, together with the obvious copycat strategy $\alpha\from\oc A\to A\sequoid\oc A$, is the final coalgebra for the endofunctor $A\sequoid\blank$.  In other words, if $B$ is a negative game and $\sigma\from B\to A\sequoid B$ is a morphism then there is a unique morphism $\fcoal{\sigma}\from B\to \oc A$ such that the following diagram commutes:
  \[
    \begin{tikzcd}
      B \arrow[r, "\sigma"] \arrow[d, "\fcoal{\sigma}"']
        & A \sequoid B \arrow[d, "\id_A\sequoid\fcoal{\sigma}"] \\
      \oc A \arrow[r, "\alpha"']
        & A \sequoid \oc A
    \end{tikzcd}
    \]
\end{proposition}
\begin{proof}
  See \cite{martinsthesis}.  We shall shortly give a proof in the more general case.
\end{proof}

@@

We want to deduce the fact that $\oc A\xrightarrow{\mu}\oc A\tensor\oc A$ is the cofree commutative comonoid on $A$ from the fact that $\oc A$ is the final coalgebra for $A\sequoid\blank$.  It turns out that we shall need one more fact about the category of games to prove this.

@@

@@

It is well known (see \cite{finalseq}, for instance) that if $j_\delta^{\delta+1}$ is an isomorphism for some $\delta$, then $j_\delta^{\delta+1}\inv\from A^{\sequoid\delta}\to A\sequoid A^{\sequoid\delta}$ is the final coalgebra for the functor $A\sequoid\blank$.  In this case, we say that the sequence \emph{stabilizes at $\delta$}.  Our proof strategy is therefore to show that the sequence stabilizes at some $\delta$, and to show that $A^{\sequoid\delta}$ is isomorphic to $\oc A$.
